Figures for conference paper

### 2019-06-07 Pillar_2_-_Topic_Modeling.Rmd
passed files to app

---
title: "Pillar 2 - Topic Modeling"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/",
                      eval = FALSE)
```

```{r library, message = FALSE, eval = TRUE}
library(tidyverse)
library(tidytext)

library(ggwordcloud) # Word Clouds
library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang)
library(ldatuning) # ideal number of topics in LDA

library(modelr) #cross_validation
```

```{r function reorder_within & co., echo = FALSE}

# Function for ordering within facet:
# https://github.com/dgrtwo/drlib/blob/master/R/reorder_within.R

reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
  new_x <- paste(x, within, sep = sep)
  stats::reorder(new_x, by, FUN = fun)
}

scale_x_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
}

scale_y_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_y_discrete(labels = function(x) gsub(reg, "", x), ...)
}
```

# Setup
We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
For `d_description` and `d_overview`, we keep only the most recent year.
```{r import data, eval = TRUE}
load("output/data_pillar_2.RDATA")

# Only keep course descriptions and overviews from most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```

# TF-IDF
## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
compute_tf_idf <- function(data){

  data %>%
    count(
      `Course ID`,
      word
      ) %>%
    bind_tf_idf(
      term = word, 
      document = `Course ID`,
      n = n
      )

}

tf_idf_description <- compute_tf_idf(d_description)
tf_idf_overview    <- compute_tf_idf(d_overview)
tf_idf_manual      <- compute_tf_idf(d_manual)

rm(compute_tf_idf)
```

The function `plot_tf_idf` plots a bar-graph of the most important words for each level of granularity and  their corresponding word clouds. 
```{r plot_tf_idf}
plot_tf_idf <- function(data, n_col = 5, id_plot = NULL){

  #
  # Barplot
  g <- data %>%
    ggplot(
      aes(
        x = reorder_within(word, tf_idf, facet), 
        y = tf_idf
        )
      ) +
    geom_col(
      show.legend = FALSE
      ) +
    labs(
      x = NULL,
      y = "tf-idf"
      ) +
    scale_x_reordered() +
    facet_wrap(
      facets = ~ facet, 
      scales = "free",
      ncol = n_col
      ) +
    coord_flip()

  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)

  #
  # Word Cloud
  g <- data %>%
    group_by(
      facet
      ) %>%
    mutate(
      freq = tf_idf / sum(tf_idf)
      ) %>% # normalization within facet
    ggplot(
      aes(
        size = freq ^ 0.7, 
        label = word, 
        color = freq ^ 0.7
        )
      ) +
    geom_text_wordcloud_area(
      area_corr_power = 1,
      eccentricity    = 1,
      rm_outside      = T
      ) +
    scale_radius(
      range = c(2, 10),
      limits = c(0, NA)
      ) +
    scale_color_gradient(
      low = "red", 
      high = "blue"
      ) +
    facet_wrap(
      facet = ~ facet,
      ncol = n_col
      ) + 
    theme(
      strip.text.x     = element_text(),
      panel.background = element_rect(fill = "white"),
      plot.title       = element_text(hjust = 0.5)
    )

  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)

}
```

## Course Level
The function `prepare_tf_idf_course` selects 25 random courses, the top ten words with highest tf_idf, and finally renames a facet to 'Course ID').
We apply the function to `id_plot` and pipe it to produce graphs.
```{r tf-idf course, cache = TRUE}
prepare_tf_idf_course <- function(data){

  data %>%

    # Selection 25 courses randomly
    filter(
      `Course ID` %in% sample(
        x = unique(.$`Course ID`),
        size = 25, 
        replace = FALSE
        )
      ) %>%

    # Select top 10 words per course 
    group_by(
      `Course ID`
      ) %>%
    filter(
      n >= 2
      ) %>%
    top_n(
      n = 10,
      wt = tf_idf
      ) %>%
    ungroup %>%

    # Prepare data for function `plot_tf_idf()`
    rename(
      facet = `Course ID`
      )

  }

set.seed(123)
tf_idf_description %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_description")

set.seed(123)
tf_idf_overview %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_overview")

set.seed(123)
tf_idf_manual %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_manual")

rm(prepare_tf_idf_course)
```

## Cluster Level
```{r tf-idf cluster, cache = TRUE}
prepare_tf_idf_cluster <- function(data){

  data %>%

    # Include the variable Cluster
    left_join(
      select(d_course, `Course ID`, Cluster),
      by = "Course ID"
      ) %>%
    filter(
      !is.na(Cluster)
      ) %>%

    # Select top 10 words per cluster
    group_by(
      Cluster, 
      word
      ) %>%
    summarise(
      tf_idf = sum(tf_idf),
      n = sum(n)
      ) %>%
    filter(
      n >= 10
      ) %>%
    top_n(
      n = 10, 
      wt = tf_idf
      ) %>%
    ungroup %>%

    # Prepare data for function `plot_tf_idf()`
    rename(
      facet = Cluster
      )

}

tf_idf_description %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_description")

tf_idf_overview %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_overview")

tf_idf_manual %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_manual")

rm(prepare_tf_idf_cluster)
```

## Concentration Level
```{r tf-idf concentration, cache = TRUE}
prepare_tf_idf_concentration <- function(data){

  data %>%

    # Include the variable Concentration
    left_join(
      select(d_course, `Course ID`, Concentration, `Concentration (additional)`),
      by = "Course ID"
      ) %>%
    filter(
      !is.na(Concentration)
      ) %>%
    gather(
      key = X,
      value = Concentration,
      Concentration, `Concentration (additional)`,
      na.rm = TRUE
      ) %>%

    # Select top 10 words per cluster
    group_by(
      Concentration, 
      word
      ) %>%
    summarise(
      tf_idf = sum(tf_idf),
      n = sum(n)
      ) %>%
    filter(
      n >= 10
      ) %>%
    top_n(
      n = 10,
      wt = tf_idf
      ) %>%
    ungroup %>%

    # Prepare data for function `plot_tf_idf()`
    rename(
      facet = Concentration
      )

}

tf_idf_description %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_description")

tf_idf_overview %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_overview")

tf_idf_manual %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_manual")

rm(prepare_tf_idf_concentration, plot_tf_idf,
   tf_idf_description, tf_idf_overview, tf_idf_manual)
```

# LDA
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdmxxxxx}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

d_description_cast <- my_cast_tdm(d_description)
d_overview_cast <- my_cast_tdm(d_overview)
d_manual_cast <- my_cast_tdm(d_manual)

rm(my_cast_tdm)
```

## Ideal Number of Topics (RUN ON UM COMPUTER)
To decide the number of topics to discover, we run (four) three different tests.

First we set the control for the test.
```{r controls, eval = TRUE}
my_control <- list(

  nstart = 20,
  seed   = 1 : 20,
  best   = TRUE,

  burnin = 1000,
  iter   = 15000,
  thin   = 100

)
```

```{r fast control}
my_control_fast <- list(

  nstart = 1,
  seed   = 1,
  best   = TRUE,

  burnin = 5,
  iter   = 10,
  thin   = 2

)
```

###With Package built in Function
The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

  FindTopicsNumber(

  dtm = data_cast,
  topics = n_topics,
  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 4L

  )

}
```
We run the test for descriptions, documenting the duration (starting_time - ending_time). We build 95 models (5 to 100 in increments of 1).
```{r description topics, cache = TRUE}
start.time <- Sys.time()

result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))

end.time <- Sys.time()
time.taken <- end.time - start.time

save(result_description,
     file = "Output/LDA_ntopics.RDATA")

print(time.taken)
```

We run the test for overview, documeting its duration. 
```{r overview topics, cache = TRUE}
start.time <- Sys.time()

result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))

end.time <- Sys.time()
time.taken <- end.time - start.time

save(result_overview , result_description,
     file = "Output/LDA_ntopics.RDATA")

print(time.taken)
```

We run the test for manuals, documenting its duration.
```{r manual topics, cache = TRUE}
start.time <- Sys.time()

result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 75, by = 5))

end.time <- Sys.time()
time.taken <- end.time - start.time

save(result_manual, result_overview , result_description,
     file = "Output/LDA_ntopics.RDATA")

print(time.taken)
```

from 20, to 40, by 5 topics takes
22min for overview
11min for description
5.5hrs for manuals

We examine the result of the experiment by plotting them on a graph.
```{r LDA number topics plot}

load("Output/LDA_ntopics.RDATA")

result_description %>%
  FindTopicsNumber_plot

result_overview %>%
  FindTopicsNumber_plot

result_manual %>%
  FindTopicsNumber_plot

```
From the results we see that the ideal number of topics is somewhere between 35 and 40.

## Fitting Model
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdm, eval = TRUE}
my_cast_tdm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

d_cast <- d_text %>% map(my_cast_tdm)

rm(my_cast_tdm)
```

The function `my_LDA` fits an LDA model on the DTM using the previous controls.
```{r my_LDA, eval= TRUE}

#my_LDA
my_LDA <- function(n_topics, corpus, control = my_control){

  LDA_model <- LDA(
    x       = corpus,
    k       = n_topics,
    method  = "Gibbs",
    control = control
    )
}

```

Next we train our model with different number of topics.
```{r LDA fit, cache = TRUE, eval = TRUE}
topic_model <- tibble(

  n_topic = seq(from = 5, to = 250, by = 5)

  ) %>%

  mutate(
    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
  )
```

##Model Evaluation
###Perplexity
Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
```{r perplexity function, eval = TRUE}

#perplexity Function
my_perplexity <- function(model, d_cast){
  perplexity(model, d_cast, estimate_theta = FALSE)
}

#Get perplexity
test_perplexity <- topic_model %>%
  mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
         perplex_manual   = map(.x = TM_manual,   .f = my_perplexity, d_cast$manual))
```

###log_likelihood
```{r log likelihood, eval = TRUE}
# #my_loglikelihood function
# my_loglike <- function(model){
#   return(model@loglikelihood)
# }
# 
# #get loglikelihood
# test2 <- topic_test %>% mutate(loglike_overview    = map(.x = TM_overview, .f = my_loglike),
#                                   loglike_manual   = map(.x = TM_manual,   .f = my_loglike))

#Log likelihood:
test_likelihood <- topic_test %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
                               logLik_manual   = map(.x = TM_manual,   .f = logLik))

```

###Plots
```{r perplexity plots, eval = TRUE}
#perplexity
plot(topic_test$n_topic, topic_test$perplex_overview)
plot(topic_test$n_topic, topic_test$perplex_manual)

#log likelihood
plot(test3$n_topic, test3$logLik_overview)
plot(test3$n_topic, test3$logLik_manual)
```

##Get Beta/Gamma functions
```{r getting gamma and beta, eval = TRUE}
get_beta <- function(results){

  tidy(results, matrix = "beta")           %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(beta) )

}

get_gamma <- function(results){

  tidy(results, matrix = "gamma")          %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(gamma) )
}

```

##Apply beta and gamma
```{r applying get_gamma and get_beta, eval = TRUE}
topic_model_gb <- topic_model %>%
  transmute(
    n_topic    = n_topic,
    g_overview = TM_overview %>% map( .f = get_gamma),
    g_manual   = TM_manual   %>% map( .f = get_gamma),
    b_overview = TM_overview %>% map( .f = get_beta),
    b_manual   = TM_manual   %>% map( .f = get_beta)
      )
```
##Saving filed for different sessions
```{r saving, eval = TRUE}
save(topic_model_gb, 
     file = "Output/topic_model_gb.RDATA")
```
#Distributions
#NOTE: We need to select how many topics to use
##Distributions of best models
```{r Distributions, eval = FALSE}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40

#Crop models
TM_overview <- topic_model_gb %>%
  filter(n_topic== n_topics_overview)

TM_manual   <- topic_model_gb %>%
  filter(n_topic== n_topics_manual)

#Distributions
distribution <- list()

distribution$beta$overview  <- TM_overview %>% pull(b_overview)
distribution$beta$manual    <- TM_manual   %>% pull(b_manual)

distribution$gamma$overview <- TM_overview %>% pull(g_overview)
distribution$gamma$manual   <- TM_manual   %>% pull(g_manual)

```
##Inspect topics
THE TOPICS ARE SUPPER STRANGE!
```{r inspect topics, eval = FALSE}

inspect_topics <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta)

}

topics <-  lapply(
  distribution$beta,
  inspect_topics
)
```
#App
##Selectig keywords
```{r key words}
get_top_words <- function(d_beta, n = 5){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

kw <- lapply(
  distribution$beta,
  get_top_words
)
```
####TEMPORTARY: stopwords for keywords
This section is for presentations
```{r stopwords for kw}
#kw$overview
not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")

remove_words <- function(x){
  setdiff(x, not_include)
}

kw1 <- lapply(
  kw,
  remove_words
)

```
##Convenience vectors for APP
```{r for convenience}
# set seed
set.seed(1)

#
## All courses
course_all <- d_course %>%
  inner_join(
    d_transcript,
    by = "Course ID"
  ) %>%
  distinct(
    `Course ID`
  ) %>%
  # remove semester abroad, skills and projects
  filter(
    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
  ) %>%
  pull

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort
```
## Saving files for APP
```{r app files}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
```

# Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){

  data.frame(d_beta) %>%
    mutate(topic = paste("Topic", topic)) %>%
      group_by(topic) %>%
        top_n(10, beta) %>%
      ungroup %>%
      arrange(topic, desc(beta))

} #repetition??? of inspect topics?

prepare_data_LDA_gamma <- function(d_gamma, level = Course){

  data_gamma <- data.frame(d_gamma) %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(`Course ID` = document)

  if(ensym(level) == sym("Course")) data_gamma <- data_gamma %>%
                                      rename(facet = `Course ID`)

  if(ensym(level) == sym("Cluster")) data_gamma <- data_gamma %>% 
                                       left_join(select(d_course, `Course ID`, Cluster), by = "Course ID") %>%
                                       filter(!is.na(Cluster)) %>%
                                       rename(facet = Cluster)

  if(ensym(level) == sym("Concentration")) data_gamma <- data_gamma %>%
                                             left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
                                             gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                             rename(facet = Concentration)

  data_gamma <- data_gamma %>%
    group_by(facet, topic) %>%
      summarise(gamma = sum(gamma)) %>%
    filter(gamma > 0.05) %>%
    ungroup %>%
    arrange(facet, desc(gamma))

  return(data_gamma)

}

# Bet Distribution
test <- list()

a <-  names(distribution)[1]
test[[a]] <- lapply(distribution[[a]],
                      prepare_data_LDA_beta)

# Gamma Distribution
b <- names(distribution)[2]
test[[b]] <- lapply(distribution[[b]],
                    prepare_data_LDA_gamma)

rm(a,b #,test
   )
```
This part is not adapted
```{r LDA visualize, eval = F}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){

  data_prepared %>%
  ggplot(aes(x = reorder_within(term,
                                by = beta,
                                within = topic),
             y = beta,
             fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, scales = "free") +
    scale_x_reordered() +
    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
    coord_flip() +
    theme_light() +
    theme(plot.title = element_text(hjust = 0.5))

  ggsave(paste(id_plot, "beta.jpeg"),
         width = 16, height = 10, path = "Plots/Topic Model")

}

visualize_LDA_gamma1 <- function(data_prepared, id_plot = "test"){

  data_prepared %>%
    ggplot(aes(reorder_within(facet, 
                              by = gamma, 
                              within = topic), 
               y = gamma, 
               fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, 
               scales = "free") +
    scale_x_reordered() +
    coord_flip() +
   # labs(x = ensym(facet), y = "Gamma", title = paste("Main", ensym(facet), "of each Topic") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

  ggsave(paste(id_plot, "gamma1.jpeg"),
         width = 16, height = 10, path = "Plots/Topic Model")

}

visualize_LDA_gamma2 <- function(data_prepared, id_plot = "test"){

  data_prepared %>%
    ggplot(aes(reorder_within(topic, 
                              by = gamma,
                              within = facet), 
               y = gamma, 
               fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ facet, 
               scales = "free") +
    scale_x_reordered() +
    coord_flip() +
  #  labs(x = "Topics", y = "Gamma", title = "Main Topics of each Courses/Cluster") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

  ggsave(paste(id_plot, "gamma2.jpeg"),
         width = 16, height = 10, path = "Plots/Topic Model")

}
```

```{r LDA visualize all distrib, eval = F}
visualize_LDA_all_distrib <- function(data, level = Course, id_plot = "test"){

  # Beta distribution
  data %>% 
    prepare_data_LDA_beta %>%
    visualize_LDA_beta(id_plot = id_plot)

  # Gamma 1 distribution
  data %>% 
    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
    visualize_LDA_gamma1(id_plot = id_plot)

  # Gamma 2 distribution
  data %>% 
    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
    visualize_LDA_gamma2(id_plot = id_plot)

}
```

```{r LDA visualize all level, eval = F}
visualize_LDA_all_level <- function(data, id_plot = "test"){

  data %>% 
    visualize_LDA_all_distrib(level = Course,
                              id_plot = paste(id_plot, "_course"))

  data %>% 
    visualize_LDA_all_distrib(level = Cluster,
                              id_plot = paste(id_plot, "_cluster"))

  data %>% 
    visualize_LDA_all_distrib(level = Concentration,
                              id_plot = paste(id_plot, "_concentration"))

}
```

### Plots
```{r LDA plot, cache = TRUE, eval = F}
load("LDA.RDATA")

LDA_description_5 %>% visualize_LDA_all_level(id_plot = "description_k5")

LDA_overview_5 %>% visualize_LDA_all_level(id_plot = "overview_k5")

LDA_manual_5 %>% visualize_LDA_all_level(id_plot = "manual_k5")
```

```{r label, eval = FALSE, eval = F}
tidy(LDA_manual_10, "beta") %>%
  filter(beta > 1e-3) %>%
  bind_tf_idf(term = term, document = topic, n = beta) %>%
  group_by(topic) %>%
  top_n(10, tf_idf) %>%
  arrange(topic, desc(tf_idf))

  count(term, topic) %>%
  arrange(desc(n)) %>%

  filter(beta > 1e-3) %>%
  group_by(term) %>%
    mutate(n_topic = n(),
           beta = beta / n_topic) %>%
  group_by(topic) %>%
    top_n(10, beta)

  count(topic, term, wt = beta) %>%
  (term = term, document = topic, n = n) %>%
  group_by(topic) %>%
  top_n(10, tf_idf)

  group_by(term) %>%
  summarise(beta = sum(beta)) %>%
  arrange(desc(beta))

labels <- list(
  description_10 = "X"
)
```

```{r label bis, eval = FALSE}
visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10 with labelled topics", facet = T,
              topic_names = c("Psychology & Information", "Economics and Development", "Biology", "Chemistry and Math",
                              "Sociology", "Law", "Research", "International Politics",
                              "Philosophy", "Humanities"))

visualize_LDA(LDA_cluster_17, id_plot = "Cluster, k = 17 with labelled topics", facet = T,
              topic_names = c("Science/Knowledge", "Psycho", "Biology", "Chemistry", "Culture",
                              "Conflict", "Research", "Foreign Policy", "Arts", "Literature",
                              "Communication Skills", "Law", "Humanities", "Computer", "Economics", 
                              "Math", "Management and ?"))
visualize_LDA(LDA_cluster_25, id_plot = "Cluster, k = 25 with labelled topics", facet = T,
              topic_names = c(
                "Information", "Psycho", "Bio", "Chem", "Sociology",
                "History", "skills", "Europe", "Philosophy", "IR",
                "Conference", "Law", "Media", "Philosophy", "Economics",
                "Math", "Management and Literature", "Entrepreneurship", "Conflict", "Research",
                "Arts", "Computer Science", "Policy?", "Physiology", "Qual. Res."))
```

>>>>

version https://git-lfs.github.com/spec/v1
oid sha256:6b7cfd788e0212b258d14cc2418c44b6ff60c64a84e3c3754cc24fc2d8e01ab1
size 24779

### 2019-06-07 conference figures.Rmd
passed files to app

---
title: "Figures for conference paper"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
editor_options: 
  chunk_output_type: console
---

# Set up

```{r setup, include = FALSE}
library(tidyverse)
library(kableExtra)
library(DiagrammeR)

knitr::opts_chunk$set(echo = FALSE)
theme_set(theme_light())

load("Output/app_model.RDATA")
load("Output/data_pillar_1.Rdata")
load("Output/d_text.RDATA")
load("Output/df_logLike_catalogue.RDATA")
load("Output/CV.RDATA")

output_folder <- "Conference/Figures"
plot_width <- 6
plot_height <- plot_width / 1.6 
```

```{r TM}
gamma <- app_model$Gamma[[1]]
beta  <- app_model$Beta[[1]]
```

```{r student_data}
set.seed(2019)

student_data <- d_transcript_augmented %>%

  select(`Student ID`, `Course ID`, `Academic Year`, Period = period_numerical, Grade) %>%

  mutate(`Student ID` = ((as.numeric(`Student ID`) + 2019) * as.numeric(`Student ID`)) %% 1e5  %>% as.character) %>% # anonymization

  sample_n(10) %>%

  arrange(`Academic Year`) %>%

  print
```

```{r}
course_data <- d_text$catalogues %>%

  slice(50005:50014) %>%

  select(`Course ID`, `Course Title`, Department = department, word) %>%

  print
```

# Student data

```{r fig_student_data}
student_data %>% 
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/student_data.pdf"))
```

# Course data

```{r fig_course_data}
course_data %>%
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/course_data.pdf"))
```

# Flow chart

```{r}
grViz("digraph flowchart{

      fontname = Helvetica
      size = 15

      node [fontname = Helvetica, shape = rectangle, style = filled, color = black, fillcolor = white]

      edge [fontname = Helvetica, decorate = TRUE]

      subgraph cluster_data {
      label = 'Data';
      style = filled;
		  color = lightgrey;
		  node [shape = cylinder];
      CD [label = 'Course Data']
      SD [label = 'Student Data']
      }

      subgraph cluster_input_user {
      label = 'User Input';
      style = filled;
		  color = coral;

      ID [label = 'Student ID']
      KW [label = 'Selected Key Words']
      CS [label = 'Selected Courses']
      }

      subgraph cluster_model_fitting{
      label = 'Model Fitting';
      style = filled;
		  color = LavenderBlush;

      TE [label = 'Topic Expertise']
      AP [label = 'Academic Performance']

      PM [label = 'Predictive Models']
      x1 [shape = circle, width = .01, height = .01, label = '']
      TM [label = 'Topic Model']

      }

      subgraph cluster_inter_last{
      label = 'Intermediate Results';
      style = filled;
		  color = Tan;

      GP [label = 'Grade Prediction']
      AI [label = 'Student´s Academic Interests']
      }

      # Ouput
      subgraph cluster_ouput {
      label = 'System Output';
      style = filled;
		  color = lightCyan;

      SUG [label = 'Course Suggestions']
      WAR [label = 'Warnings']
      PRE [label = 'Preparatory Coursework']
      }

      TR [label = 'Student´s Transcript']

      # Invisible node
      x2 [shape = circle, width = .01, height = .01, label = '']
      x3 [shape = circle, width = .01, height = .01, label = '']

      # edges

      SD -> AP [weight = 2];
      {SD, TM} -> TE;
      {TM, KW} -> AI;
      ID -> TR;
      {PM, CS, TR} -> GP;
      GP -> WAR;
		  WAR -> PRE;

      CD -> TM [label = '  LDA'];

      {AP, TE} -> x1 [arrowhead = none]
      x1 -> PM [label = '  Lasso'];

      {TM, AI} -> x2 [arrowhead = none]
      x2 -> SUG [label = '  KL distance'];

      {TM, PM} -> x3 [arrowhead = none]
      x3 -> PRE [label = '  KL distance'];

      }
      ")

# Save by hand
# image format: JPEG
# Width: 626
# Check Maintain aspect ratio
# File name: Conference/Figures/Flowchart
```

# Model Selection (topic model)

```{r}
max_LL <- df_logLike_catalogue$n_topic[which.max(df_logLike_catalogue$LogLikelihood)]

df_logLike_catalogue %>%
  ggplot(aes(x = n_topic, y = LogLikelihood)) +
  geom_vline(xintercept = max_LL, col = "red", alpha = 0.5, linetype = "dashed", size = 1) +
  geom_line(linetype = "dashed") +
  geom_point() +

  labs(title = NULL, subtitle = NULL, x = "Number of Topics", y = "Log-Likelihood") +

  ggsave(filename = str_c("Model Selection.jpeg"), path = output_folder,
         width = plot_width, height = plot_height)
```

# Beta

```{r plot_beta}
plot_beta <- function(topic = 1, resize_factor = 1){

  top <-  str_c("Topic ", topic)

  beta %>%
    filter(topic == top) %>% 
    top_n(10, beta) %>%

    ggplot() +
    geom_col(aes(x = reorder(term, beta), y = beta)) +

    coord_flip() +

    theme(axis.text.y = element_text(size = 11)) +

    labs(title = str_c("Topic ", topic),
         x = "Terms",
         y = "Beta"
         )

  ggsave(filename = str_c("Beta - topic ", topic, ".jpeg"), path = output_folder,
         width = plot_width / resize_factor, height = plot_height / resize_factor)

}
```

```{r fig_beta}
plot_beta(1)
```

# Gamma

```{r plot_gamma}
plot_gamma <- function(course = "COR1002"){

  gamma %>%
    filter(document == course) %>% 
    top_n(10, gamma) %>%

    ggplot() +
    geom_col(aes(x = reorder(topic, gamma), y = gamma)) +

    coord_flip() +

    labs(title = course,
         x = "Topics",
         y = "Gamma"
         )

  ggsave(filename = str_c("gamma - course ", course, ".jpeg"), path = output_folder,
         width = plot_width, height = plot_height)

}
```

```{r fig_gamma}
plot_gamma("COR1004")

resize_factor <- 1.6

plot_beta(4, resize_factor = resize_factor)
plot_beta(19, resize_factor = resize_factor)
```

# Topic Expertise
```{r}
courses <- paste("Course", 1 : 3)

transcript <- tibble(Course    = courses,
                     Grade     = c(6  , 9  , 2.5))

gamma <- tibble(Course    = courses,
                `Topic 1` = c(0  , 0.2, 0  ),
                `Topic 2` = c(0.7, 0.2, 0.4),
                `Topic 3` = c(0.2, 0.2, 0.2),
                `Topic 4` = c(0.1, 0.2, 0.1),
                `Topic 5` = c(0  , 0.2, 0.2))

df1 <- gamma %>% 
  gather(key = Topic, value = gamma, -Course) %>% 
  arrange(Course) %>%

  left_join(transcript, by = "Course") %>%
  mutate(contribution = Grade/10 * gamma)

topic_expertise <- df1 %>%
  select(-gamma, - Grade) %>% 
  spread(key = Topic, value = contribution)

# Table

transcript %>% 
  mutate(Grade = str_c(Grade, "/10")) %>%
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/toy_transcript.pdf"))

gamma %>% 
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/toy_gamma.pdf"))

topic_expertise %>% 
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/toy_topic_expertise.pdf"))

# Plot
df1 %>% 
  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
  geom_col() +
  labs(x = "Topics", y = "Topic Expertise")

ggsave(filename = str_c("toy Topic Expertise.jpeg"), path = output_folder,
       width = plot_width, height = plot_height)
```

# CV
```{r}
fit_lasso %>%
  ggplot(aes(y = cv_error, group = 1)) +
  geom_boxplot() +
  theme(axis.ticks.y = element_line(color = "white"),
        axis.text.y  = element_text(color = "white"),
        panel.border = element_rect(color = "white"),
        panel.grid   = element_line(color = "white")
        ) +

  labs(y = "Cross-Validation Mean Absolute Error") +
  coord_flip()

ggsave(filename = str_c("CV.jpeg"), path = output_folder,
         width = plot_width/1.5, height = plot_height/3.5)

fit_lasso %>%
  summarize(Mean = mean(cv_error),
            `Weighted mean` = weighted.mean(cv_error, n),
            Median = median(cv_error),
            `Standard Deviation` = sd(cv_error),
            Minimum = min(cv_error),
            Maximum = max(cv_error)) %>%
  gather(key = x, value = y) %>% 
  kable("latex", booktabs = TRUE, col.names = NULL) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/CV.pdf"))
```

>>>>

version https://git-lfs.github.com/spec/v1
oid sha256:8011c4bd9ae22ca4c0ce324c2c05f3b85a93bb3fb5e51a4633b9f50318bea107
size 8329
